UGAN: Improving Underwater Image Quality using Generative Adversarial Networks

### 2017-09-15 files/paper/tex/experiments.tex
Moved some sections to experiments. Added text to methodology.

\section{Experiments}
\subsection{Datasets}
We used several subsets of Imagenet~\cite{deng2009imagenet} for training and evaluation of our methods. We also evaluate a 
tracking
algorithm on a video of scuba divers taken from Youtube \footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of 
Imagenet
containing underwater images were selected for the training of CycleGAN, and manually separated into two classes based on visual
inspection. We let $X$ be the set of underwater images with no distortion, and $Y$ be the set of underwater images with 
distortion. $X$
contained 6143 images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such 
that images
from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting all images in $X$ 
with
$F$. Figure~\ref{fig:cgan_samples} shows sample training pairs. When comparing with CycleGAN, we used a test set of 56 images 
acquired from
Flickr\texttrademark .

@@

>>>>

\section{Experiments}
\label{sec:experiments}

\subsection{Datasets}
We used several subsets of Imagenet~\cite{deng2009imagenet} for training and evaluation of our methods. We also evaluate a 
tracking
algorithm on a video of scuba divers taken from Youtube \footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of 
Imagenet
containing underwater images were selected for the training of CycleGAN, and manually separated into two classes based on visual
inspection. We let $X$ be the set of underwater images with no distortion, and $Y$ be the set of underwater images with 
distortion. $X$
contained 6143 images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such 
that images
from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting all images in $X$ 
with
$F$. Figure~\ref{fig:cgan_samples} shows sample training pairs. When comparing with CycleGAN, we used a test set of 56 images 
acquired from
Flickr\texttrademark .

@@

\subsection{Training and Inference Performance}
In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer 
\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every update of the 
generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$ and $\alpha = 1$. Our implementation was done using the 
Tensorflow library \cite{abadi2016tensorflow}. \footnote{Code is available at 
\url{https://github.com/cameronfabbri/Underwater-Color-Correction}} All networks were trained from scratch on a GTX 1080 for 100 
epochs. Inference on the GPU takes on average $ 0.0138s$, which is about 72 Frames Per Second (FPS). On a CPU (Intel Core 
i7-5930K), inference takes on average $ 0.1244s$, which is about 8 FPS. We find both of these measures acceptable for underwater 
tasks.

### 2017-09-15 files/paper/tex/methodology.tex
Moved some sections to experiments. Added text to methodology.

\section{Methodology}
\label{sec:methodology}

\subsection{Dataset Generation}
Here we describe our dataset generation process. Depth, lighting conditions, camera
model, and location are all factors that affect the amount of distortion an underwater image undergoes. Under certain
conditions, it is possible that an underwater image may have very little distortion, or none at all.
We let $I^C$ be an underwater image with no distortion, and $I^D$
be the same image with distortion. Our goal is to learn the function $f: I^D \rightarrow I^C$. Becasue of the
difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist, but never both.

We use the recently proposed CycleGAN \cite{zhu2017unpaired} to generate $I^D$ from $I^C$, which gives us a paired
dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping
$F: X \rightarrow Y$. Figure ~\ref{fig:cgan_samples} shows paired samples generated from CycleGAN. From this paired dataset we 
train a
generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our data generation process,
CycleGAN simultaneously learns a mapping $G: Y \rightarrow X$, which is similar to $f$. In section IV we show a comparison with 
our method.

\subsection{Adversarial Networks}
GANs \cite{goodfellow2014generative} are a class of generative models based on game theory in which a generator
network competes against an adversary. Conditioned on an image $I^D$, the generator is trained to produce an \
image to try and fool the discriminator, which is trained to distinguish be between distorted and non-distorted
underwater images. In the original GAN formulation, our goal is to solve the minimax problem:

@@

\noindent Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this
formulation, the discriminator is hypothesized as a classifier with a sigmoid cross entropy loss function, which in
practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
hypothesize a different loss function for the discriminator
\cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}. We focus on the Wasserstein GAN
(WGAN) \cite{arjovsky2017wasserstein} formulation, which proposes to use the Earth-Mover or \textit{Wasserstein-1}
distance $W$ by constructing a value function using the Kantorovich-Rubinstein duality \cite{villani2008optimal}.
In this formulation, $W$ is approximated given a set of $k$-Lipschitz functions $f$ modeled as neural networks. To
ensure $f$ is $k$-Lipschitz, the weights of the discriminator are clipped to some range $[-c, c]$. In our work, we
adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of clipping
network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft
constraint on the gradient norm of the discriminator's output with respect to its input. Following
\cite{gulrajani2017improved}, our new objective then becomes

@@

In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer
\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every
update of the generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$ and $\alpha = 1$. Our implementation was done using 
the
Tensorflow library \cite{abadi2016tensorflow}.
\footnote{Code is available at \url{https://github.com/cameronfabbri/Underwater-Color-Correction}}
All networks were trained from scratch on a GTX 1080 for 100 epochs. Inference on the GPU takes on average $ 0.0138s$,
which is about 72 Frames Per Second (FPS). On a CPU (Intel Core i7-5930K), inference takes on average $ 0.1244s$, which
is about 8 FPS. We find both of these measures acceptable for underwater tasks.

>>>>

\section{Methodology}
\label{sec:methodology}
\starnote{A short summary of the method needs to go here, like an overview, so the reader can `stay in the loop' so to speak.}

\subsection{Dataset Generation}
Depth, lighting conditions, camera model, and physical location in the underwater environment are all factors that affect the 
amount of distortion an image will be subjected to. Under certain conditions, it is possible that an underwater image may have 
very little distortion, or none at all. To generate the dataset to train the generative model\starnote{check this please}, we let 
$I^C$ be an underwater image with no distortion, and $I^D$ be the same image with distortion. Our goal is to learn the function 
$f: I^D \rightarrow I^C$. Becasue of the difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist, 
but never both.

To circumvent the problem of insufficient image data in $I^D$, we use CycleGAN to generate $I^D$ from $I^C$, which gives us a 
paired dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping $F: X 
\rightarrow Y$. Figure~\ref{fig:cgan_samples} shows paired samples generated from CycleGAN. From this paired dataset we train a 
generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our data generation process, CycleGAN 
simultaneously learns a mapping $G: Y \rightarrow X$, which is similar to $f$. In Section~\ref{sec:experiments}, we compare images 
generated by CycleGAN with images generated through our approach.

\subsection{Adversarial Networks}
\starnote{check this paragraph as I added some more text}In machine learning literature, Generative Adversarial Networks 
(GANs)~\cite{goodfellow2014generative} represent a class of generative models based on game theory in which a generator network 
competes against an adversary. From a classification perspective, the generator network produces instances which actively attempts 
to `mislead' the discriminator network. The goal is for the discriminator network to be able to distinguish between `true' 
instances and the `false' but realistic looking instances produced by the generator network, and thus improve its classification 
accuracy. In our case, conditioned on an image $I^D$, the generator is trained to produce an image to try and confuse the 
discriminator, which is trained to distinguish between distorted and non-distorted underwater images. In the original GAN 
formulation, our goal is to solve the minimax problem:

@@

Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this formulation, 
the discriminator is hypothesized as a classifier with a sigmoid cross-entropy loss function, which in practice may lead to issues 
such as the vanish gradient and mode collapse~\starnote{Clarify?}. There have been a number of recent methods which hypothesize a 
different loss function for the discriminator
\cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}. We focus on the Wasserstein GAN
(WGAN) \cite{arjovsky2017wasserstein} formulation, which proposes to use the Earth-Mover or \textit{Wasserstein-1}
distance $W$ by constructing a value function using the Kantorovich-Rubinstein duality \cite{villani2008optimal}.
In this formulation, $W$ is approximated given a set of $k$-Lipschitz functions $f$ modeled as neural networks. To
ensure $f$ is $k$-Lipschitz, the weights of the discriminator are clipped to some range $[-c, c]$. In our work, we
adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of clipping
network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft
constraint on the gradient norm of the discriminator's output with respect to its input. Following
\cite{gulrajani2017improved}, our new objective then becomes

@@
